---
title: "NSF coverage"
author: "Brian C. O'Meara"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

This was created for NSF grants from 1980 to 2017.

I first filtered grants for those that matched "systematics", "phylogen", "taxonom", "tree of life" in their title or abstract.

Then, for each clade, I used itis to find the list of families for that clade.

All the filtered grants were filtered again for those matching the original clade name and/or any of the families in that clade.

The package [NSFgrantparser](https://bomeara.github.io/NSFgrantparser/) [by me] was used for these steps.

Those results were summarized below.

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=FALSE)
library(NSFgrantparser)
library(taxize)
library(pander)
library(rphylotastic)
library(geiger)
library(ape)
library(phytools)
library(wordcloud)
```


```{r load data, echo=FALSE, warning=FALSE}
files <- system("ls -1 GrantInfo_*.csv", intern=TRUE)
clade.names <- gsub("GrantInfo_","", gsub(".csv", "", files))
```


```{r process files, echo=FALSE, warning=FALSE}
final.df <- data.frame()
for (clade.index in sequence(length(clade.names))) {
  clade.info <- read.csv(files[clade.index], stringsAsFactors=FALSE)
  #results.dark <- rphylotastic::SeparateDarkTaxaGenbank(clade.names[clade.index])
  #local.df <- data.frame(clade=clade.names[clade.index], number.grants=nrow(clade.info), total.grants=sum(clade.info$amount), median.grant=median(clade.info$amount), mean.grant=mean(clade.info$amount), ntips.genbank = length(results.dark$dark)+length(results.dark$known), fraction.dark = results.dark$fraction.dark, PIs=paste(clade.info$PI, collapse=", "))

    local.df <- data.frame(clade=clade.names[clade.index], number.grants=nrow(clade.info), total.grants=sum(clade.info$amount), median.grant=median(clade.info$amount), mean.grant=mean(clade.info$amount), PIs=paste(clade.info$PI, collapse=", "), investigators=paste(clade.info$investigators, collapse="\t"))
  final.df <- rbind(final.df, local.df)
}
pander(final.df[,-ncol(final.df)])
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=20, fig.height=10}
plotting.df <- final.df[,-1]
rownames(plotting.df) <- final.df$clade

barplot(plotting.df$number.grants, las=2, main="Number of grants")
barplot(plotting.df$total.grants, las=2, main="Total grants")
barplot(plotting.df$mean.grant, las=2, main="Mean grant")
```



```{r build tree, echo=FALSE, warning=FALSE, message=FALSE}
phy <- rphylotastic::GetOToLTree(clade.names)
for (i in sequence(ape::Ntip(phy))) {
  phy$tip.label[i] <- strsplit(phy$tip.label[i], "_")[[1]][1]
}
total.grant.char <- final.df$total.grants
names(total.grant.char) <- final.df$clade
pruned <- geiger::treedata(phy, total.grant.char)
pruned$phy <- ape::compute.brlen(pruned$phy)
phytools::contMap(pruned$phy, log(pruned$data[,1]))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
for (i in sequence(nrow(final.df))) {
  cat(as.character(final.df$clade[i]))
  wordcloud((strsplit(as.character(final.df$PIs[i]), ", ")[[1]]), main=final.df$clade[i])
}
```
